---
title: "Intro of StatComp21012"
author: "ZengMin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro of StatComp21012}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



# Model：

The goal of many studies in biomedical and social science is to estimate the causal effects of a binary treatment $\mathbf{Treat}$ on an outcome $\mathbf{Y}$ from the observational data. However, observational datas like electronic health records (EHR) are often with misclassification problem and selection bias problem. To overcome this issue, we proposed a adjusted method and combined it with the most commonly used methods for estimating Average Treatment Effect, like IPTW, Double Robust, logit regression and spline regression. We compared our methods with the naive
IPTW method in simulation study. Results shows our methods are better.


The selection bias parameter $S$ and The misclassification parameter $P$ are defined as followed：

The selection bias parameter $S$
$$
S_{01}=P(S=1|Y=0);\\
S_{11}=P(S=1|Y=1);\\
$$
The misclassification parameter $P$
$$
P_{11}=P(Y^*=1|Y=1);\\
P_{01}=P(Y^*=1|Y=0);\\
$$

The propensity score model:

$$P(T=1|X)=expit(\beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3)$$

The outcome model:

$$
\begin{aligned}
&P(Y=1 \mid X, T)=\operatorname{expit}\left(\gamma_{0}+\gamma_{1} X_{1}+\gamma_{2} X_{2}+\gamma_{3} X_{3}+\gamma_{T} T\right) 
\end{aligned}
$$


## Simulation Set

$$
\beta_0 = -1, \ \ \beta_1 = 0.02,\ \ \beta_2 = 0.2,\ \  \beta_3=0.1
$$
$$
\gamma_0 = -1,\ \  \gamma_1 = 0.01, \ \ \gamma_2 = 0.1, \ \ \gamma_3 = 0.05, \ \ \gamma_t = 0.5
$$
$$
s_{01} =0.7,\ \ s_{11} = 0.9;\   \   \    p_{01}  = 0.2, \ \ p_{11} = 0.9
$$
$$
n = 1000, \ \ m = 200
$$

## Simulation result

```{r}
library(StatComp21012)
```

```{r echo=FALSE}
  library(StatComp21012)
  # # p01 = 0.1; p11 = 0.9 
  # # s01 = 0.6; s11 = 0.9
  # 
  n = 1000 #sample number

  M <- 200#simulation times
  
  ##naive method
    naive <- function(dtset){
      nE1 <- mean( dtset$Treat * dtset$Y/dtset$ehat)
      nE2 <- mean((1-dtset$Treat)*dtset$Y/(1-dtset$ehat))
      return(nE1-nE2)
    }
  # propensity score model
  beta0 = -1; beta1 = 0.02; beta2 = 0.2; beta3 = 0.1

  # outcome model
  gama0 = -1; gama1 = 0.01; gama2 = 0.1; gama3 = 0.05; gamat = 0.5

  # The logistic function 
  expit <- function(x){exp(x)/(1+exp(x))}
  
  misspecified<-function(Y, p){
    # Y is the original outcome, return the mis specified outcome Y_star.
    # Y been an binary variable with elements in c(1, 0)
    # p is a vector with two components p01 and p11.
    p01 <- p[1]
    p11 <- p[2]
    n <- length(Y)
    Y_star <- c()
    for(i in 1:n){
      if(Y[i]==1)
        Y_star[i] <- sample(c(1, 0), 1, prob = c(p11, 1-p11)) 
      if(Y[i]==0)
        Y_star[i] <- sample(c(1, 0), 1, prob = c(p01, 1-p01))
    }
    return(Y_star) 
  }
  
  selection <- function(Y, s){
    # Y is the original outcome, return the selection indicator ind.
    # Y been an binary variable with elements in c(1, 0)
    # s is a vector with two components s01 and s11.
    s01 <- s[1]
    s11 <- s[2]
    ind <- c()
    n <- length(Y)
    for(i in 1:n){
      if(Y[i]==1)
        ind[i] <- sample(c(1, 0), 1, prob = c(s11, 1-s11))
      if(Y[i]==0)
        ind[i] <- sample(c(1, 0), 1, prob = c(s01, 1-s01))
    }
    return(ind)
  }
```

```{r echo=FALSE}
# Generate data function
  Generatedt <- function(s, p, beta, gama, n){
    X1 <- runif(n, 0, 80)                                   #age
    X2 <- rbinom(n, 1, 0.5)                                 #sex
    X3 <- sample(c(1:4), n, replace = T, prob = rep(0.2, 4))#race
    #parameters of propensity score model.
    beta0 = beta[1]; beta1 = beta[2];
    beta2 = beta[3]; beta3 = beta[4];
    # e been the perpencity score of each patient.
    e <- expit(beta0 + beta1*X1 + beta2*X2 + beta3*X3)
    # Generate True Treatment
    Treat <- c()
    for (i in 1:n) {
      Treat[i] <-  sample(c(1,0), 1, replace = T,  prob = c(e[i],1-e[i]))
    }
    #parameters of outcome model.
    gama0 = gama[1];gama1 = gama[2];gama2 = gama[3];
    gama3 = gama[4];gamat = gama[5];
    # outcome model
    P_y <- expit(gama0 + gama1*X1 + gama2*X2 + gama3*X3 + gamat*Treat)
    # The true Outcome for each patient.
    Y <- c()
    for(i in 1:n){
      Y[i] <- sample(c(1, 0), 1, replace = T, prob = c(P_y[i], 1-P_y[i]))
    }
    ## the misspecification parameters.
    p01 = p[1];p11 = p[2]
    ## The selection bias parameters.
    s11 = s[1];s01 = s[2]
    ##The observed outcome and selection indicators
    Y_star <- misspecified(Y,  p)
    ind <- selection(Y, s)
    dt <- data.frame(Treat = Treat, Y = Y_star, X1, X2, X3, ind, e)
    dt <- dt[dt$ind==1,]
    return(dt)
  }
```

```{r echo=FALSE}
## the TRUR value
gama <- c(gama0, gama1, gama2, gama3, gamat)
ghat1 <- function(x){
  expit(gama[1] + sum(gama[2:4]*x) + gama[5]*1)
}
ghat0 <- function(x){
  expit(gama[1] + sum(gama[2:4]*x) + gama[5]*0)
}
f1 <- function(x){(ghat1(x)-ghat0(x))}
f2 <- function(x){y1 <- sample(c(1,0), 1, replace = T, prob = c(ghat1(x),1-ghat1(x)))
y0 <- sample(c(1,0), 1, replace = T, prob = c(ghat0(x),1-ghat0(x)))
return(y1-y0)}
#integrate by Monte Carlo Method
B = 100000
inte_x1 <- runif(B, 0, 80)
inte_x2 <- rbinom(B, 1, 0.5) 
inte_x3 <- sample(c(1:4), B, replace = T, prob = rep(0.25, 4))
te <- cbind(inte_x1, inte_x2, inte_x3)
Truevalue = mean(apply(te, 1, f1))
```

```{r warning=FALSE}
  p01 = 0.2; p11 = 0.9 
  s01 = 0.7; s11 = 0.9
  ATE_IPTW <- c()
  ATE_naive <- c()
  ATE_Para <- c() 
  ATE_DR <- c()
  ATE_Spline <- c()
  for(i in 1:M){
  dt <- Generatedt(s = c(s01, s11), 
                     p = c(p01, p11),
                     beta = c(beta0, beta1, beta2, beta3), 
                     gama = c(gama0, gama1, gama2, gama3, gamat),
                     n = n)
  ##input dataset with Treat: treament, Y: outcome, X1, X2, X3:covariates.
  ## s01, s11, p01, p11.
  ## return the estimated ATE
  gfit <- glm(formula = Y~X1+X2+X3+Treat, 
                family = binomial(link = "logit"),
                data = dt)
  efit <- glm(formula = Treat~X1+X2+X3,
              family = binomial(link = "logit"),
              data = dt)
  dt$ehat <- predict(efit, type = "response")
  ATE_naive[i] <- naive(dt)
  ATE_IPTW[i] <- IPTWmethod(dt, Treat, Y, ehat, s01, s11, p01, p11)
  ATE_Para[i] <- paramethod(gfit, s01, s11, p01, p11)
  ATE_DR[i] <- DRmethod(dt, gfit,Treat, Y, ehat, s01, s11, p01, p11)
  ATE_Spline[i] <- splinemethod(dt, s01, s11, p01, p11)
  }
  result <- data.frame(Naive = ATE_naive,IPTW = ATE_IPTW, 
                      DR = ATE_DR, Para = ATE_Para,
                     Spline=ATE_Spline)
  boxplot(result)
  abline(h = Truevalue, col="red")
  RelativeBias <- round((colMeans(result)-Truevalue)/Truevalue*100,5)
  MSE <- round(apply(result, 2, function(x){mean((x-Truevalue)^2)}), 5)
  result4 <- rbind(RelativeBias, MSE)
  print(rbind(RelativeBias, MSE))
```



